---
title: "HW3anaLR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HW3anaLRe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(HW3anaLR)
```

## Introduction

This vignette demonstrates how to use the HW3anaLR package to fit multiple linear regression models and perform diagnostic analysis.

## Fitting a Model

You can fit a model using the my_multi_lm function:

```R
# Simulated data
set.seed(123)
data <- data.frame(x1 = rnorm(100), x2 = rnorm(100), y = rnorm(100))
# Fit model
result <- my_multi_lm(y ~ x1 + x2, data = data)
print(result)
```

## Diagnostic Analysis

After fitting the model, you can perform diagnostics to check for potential issues:

```R
# Conduct diagnostics
diagnostics <- multi_lm_diag(model_results = result)
print(diagnostics)
```

## Comparisons

I. Correctness
Compare the results from my_multi_lm to R’s built-in lm function to ensure correctness:

```R
lm_result <- lm(y ~ x1 + x2, data = data)
all.equal(summary(lm_result)$coefficients, result$coefficients)
```

II. Efficiency
Compare the efficiency of my_multi_lm against lm using the microbenchmark package:

```R
library(microbenchmark)
benchmark <- microbenchmark(
  my_multi_lm = my_multi_lm(y ~ x1 + x2, data = data),
  lm = lm(y ~ x1 + x2, data = data),
  times = 100
)
print(benchmark)
```



